% Chris Gibson's Resume
% URL: 
%
% Based on resume tex file by Kamil Wojcicki
% URL: http://linux.dsplabs.com.au/resume-writing-example-latex-template-linux-curriculum-vitae-professional-cv-layout-format-text-p54/

\documentclass[margin,line]{resume}

\usepackage{graphicx}

\begin{document}

\name{\Huge Ivan Dimitrov}
{
	\sc
    \hfill 0885 452 670		  \vspace{0mm}\\\vspace{0mm}%
    \hfill ivan.v.dimitrov@pm.me        \vspace{0mm}\\\vspace{0mm}%
    \hfill github.com/vanjiii		\vspace{0mm}\\\vspace{-10mm}%
}

\begin{resume}

\vspace{1mm}

    %__________________________________________________________________________________________________________________
    % Interests
    \section{\mysidestyle \textbf{\large{A}\small{BOUT}}}

    I am a backend software developer who enjoys working in a high energy environment using modern technologies. I am used to applying agile methodologies, breaking down user requirements into tasks, teaching junior developers. Some of the technologies used daily are Golang, PostgreSQl, GraphQL and RESTFul services. I am familiar with git, docker, LaTeX and NoSQL databases as well. I am not afraid of making decisions and taking responsibility. I have also experience with enterprise projects using Java and Android.

\sectionline

    %__________________________________________________________________________________________________________________
    % Computer Skills
    \section{\mysidestyle \textbf{\large{S}\small{KILLS}}}

    Golang,\hspace{2mm}PostgreSQL,\hspace{2mm}GraphQL,\hspace{3mm}RESTFul services.

\sectionline

    %__________________________________________________________________________________________________________________
    % Professional Experience
    \section{\mysidestyle \textbf{\large{P}\small{ROFESSIONAL\\EXPERIENCE}}}

    % Zoox Engineering Manager
    \textbf{\listing StageAI}, Sofia \vspace{2mm}\\\vspace{1mm}%
    \textsl{Senior Software Developer} \hfill \textbf{May 2020 -- Present}\\
    \begin{list2}
        \item Breakdown tasks and requirements.
        \item Helping and teaching juniors colleagues.
	\item Supervise the working processes applying agile methodologies.
	\item Apply and encourage of using practices from 'Extreme Programming'. 
    \end{list2}

    % Zoox Software Developer
    \textsl{Software Developer} \hfill \textbf{Jan 2018 -- May 2020}\\
    \begin{list2}
        \item Developed various web application using mainly with Golang, SQL and NoSQL dbs, REST and Graphql.
	\item Deliver high quality code using TDD. 
    \end{list2}

    % Zoox Engineering Manager
    \textbf{\listing Musala Soft}, Sofia \vspace{2mm}\\\vspace{1mm}%
    \textsl{Software developer} \hfill \textbf{Aug 2016 -- Dec 2017}\\
    \begin{list2}
        \item Worked as a contractor for Experian maintaining their existing project using mainly internal tools in the Java ecosystem.
    \end{list2}

    % Zoox Software Developer
    \textsl{Junoir Software Developer} \hfill \textbf{Aug 2015 -- Aug 2016}\\
    \begin{list2}
        \item Developed native android applications with Java.
        \item Maintained hybrid mobile applicatrion with Javascript and apache Cordova.
	\item Maintained Java enterpise application using JSP, maven, OracleDB.  	
    \end{list2}

    % CreateSpace
	\textbf{\listing Game developer{-}intern}, Varna \vspace{2mm}\\\vspace{1mm}%
    \textsl{Software Developer} \hfill \textbf{Aug 2014 -- Sept 2014}
    

\sectionline

    %__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle \textbf{\large{E}\small{DUCATION}}}

    \textbf{\listing Technical University}, Varna \vspace{2mm}\\\vspace{1mm}%
    \textsl{M.S of Computer Science} \hfill \textbf{ Sep 2013 -- June 2015}\\
    \textsl{B.S of Electronics} \hfill \textbf{ Sep 2009 -- June 2013}\\

\sectionline

    % _________________________________________________________________________________________________________________
    % Certifications
    \section{\mysidestyle \textbf{\large{C}\small{ERTIFICATIONS}}}

    \textbf{Oracle Certified Professional}, Oracle \hfill \textbf{Sep 2017} \vspace{2mm}\\\vspace{1mm}%
    \textbf{Agile Software Developement}, The Business Institute \hfill \textbf{Apr 2017} \vspace{2mm}\\\vspace{1mm}%
    \textbf{Managing Team Performance}, The Business Institute \hfill \textbf{Feb 2017} \vspace{2mm}\\\vspace{1mm}%
    \textbf{Oracle Certified Associate}, Oracle \hfill \textbf{Nov 2016} \vspace{2mm}\\\vspace{1mm}%

\end{resume}
\end{document}
